---
title: "CONNECT Annual Report"
author: "Ethan Tenison"
date: "`r format(Sys.Date(), '%B %d, %Y') `"
output:
  bookdown::html_document2:
    toc: yes
    toc_float: yes
    toc_depth: 3
    collapsed: no
    number_sections: yes
    fig_caption: yes
always_allow_html: yes
editor_options:
  chunk_output_type: console
runtime: shiny
resource_files:
- references/images/RGB_formal_RGK.png
---


```{r setup, include=FALSE}
library(shiny)

library(bookdown)
library(officer)
library(officedown)

library(tm)
library(wordcloud)
library(wordcloud2)
library(NLP)

library(tidyverse)

# render tables
library(kableExtra)
library(flextable)

library(scales)
library(extrafont)
library(ggpubr)
library(hablar) # Easily change column type
library(extrafont)
library(lubridate)
library(plotly)
library(ggthemes)
library(DT)
library(htmlwidgets)
library(data.table)
library(htmlwidgets)
library(readxl)
library(igraph)
library(ggraph)
library(visNetwork)

knitr::opts_chunk$set(echo = FALSE, dpi = 300)
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
```

```{r htmlTemplate, echo=FALSE}
# Create the external file
htmltools::img(src = knitr::image_uri("C:/Users/tenis/Desktop/Data_Projects/CONNECT_Annual_Report/references/images/RGB_formal_RGK_resized.png"), 
               alt = 'logo', 
               style = 'position:absolute; top:50px; right:1%; padding:10px;z-index:200;')


```



```{r constants, include=FALSE}

color_hd <- "#00a9e0"  
color_font <- "#283e36"
color_bg <- "#eff2f1"
color_red <- "#e00034"
color_blue <-  "#0f4dbc"
```



```{r my_functions, include=F}



# glue is better
fn_text <- function(txt, color = color_font, size_px = 15)
  glue::glue('
             <span style="
              color:{color}; 
              font-size: {size_px}px">
              {txt}
             </span>')


```

<br>

# Introduction

The purpose of this document is to provide updates on the CONNECT Program during year 3 of it's development

# CONNECT Program Network 

Since it's inception in 2018, CONNECT has partnered with 80 unique organizations. 

```{r network_viz, include = T}

set.seed(32)

network_raw <- read_excel("data/interim/raw_network.xlsx") |> 
  distinct()

g1<-graph_from_data_frame(d=network_raw,directed=TRUE) 

#Getting the total number of connections
TotalDegree<- as.data.frame(igraph::degree(g1)) |> 
   tibble::rownames_to_column("id") |> 
   dplyr::rename("partnerships" = "igraph::degree(g1)")


#Ploting a basic network graph with igraph dataframe 
plot(g1, edge.color = "slateblue", edge.width = E(g1)$weight, layout = layout_nicely, vertex.label = ifelse(igraph::degree(g1) > 4, V(g1)$name, NA), vertex.size = sqrt(igraph::degree(g1) * 2), vertex.label.color = "black", vertex.label.font = 2, vertex.label.degree = 1.5, vertex.label.cex = 1.3, asp = -5, vertex.color = "gold") # vertex.frame.color = "gold"
title("NPO Network", cex.main = 3)


#converting network data of edges and nodes to dataframes for easier analysis 
gvis<-toVisNetworkData(g1)

edges <- gvis$edges |> 
  left_join(TotalDegree, by = c("from" = "id"))

edges <- edges[sample(nrow(edges)),]

#Program Colors
program_colors <- c("#efb346",
                    "#17a769",
                    "#cd023d",
                    "#852f88",
                    "#4e54ac",
                    "#0f8096",
                    "#e8351e"
                    )


names(program_colors) <- c(
  "CONNECT",
  "Mission Squared",
  "Austin Together Fund",
  "Mission Capital",
  "Good Measure",
  "E3 Alliance",
  "AmeriCorps"
)


#Creating a column to indicate which edge should be opaque   
main <- edges |> 
  distinct(from, .keep_all = TRUE) |> 
  select(from, to) |> 
  mutate(main = TRUE)

edges <- edges |>
  left_join(main, by = c("from", "to")) |>
  mutate(main = tidyr::replace_na(main, FALSE)) |> 
  mutate(main = case_when(
    from == "College Forward" & to == "AmeriCorps" ~ FALSE,
    from == "College Forward" & to == "Mission Capital" ~ TRUE,
    from == "CIS" & to == "AmeriCorps" ~ TRUE,
    from == "CIS" & to == "CONNECT" ~ FALSE, 
    main ~ main
  ))

	
nodes <- edges |> 
  filter(main == TRUE) |> 
  select(from, to, partnerships) |> 
  dplyr::rename("node" = "from", "program" = "to") |> 
  rbind(c("CONNECT", "CONNECT", 80),
        c("AmeriCorps", "AmeriCorps", 9)) 

nodes$partnerships <- as.numeric(nodes$partnerships)

#separating nodes for inner and outer layout
nodes_outer <- nodes |> 
  filter(partnerships < 7) |> 
  mutate(level = 1)

# number of nonprofits to display in outer ring
number_of_nonprofits <- 297

nodes_inner<- nodes |> 
  filter(partnerships > 6) |> 
  mutate(program = ifelse(node == "Austin Together Fund", "Austin Together Fund", program),
         program = ifelse(node == "Mission Squared", "Mission Squared", program),
         program = ifelse(node == "Good Measure", "Good Measure", program), 
         program = ifelse(node == "Mission Capital", "Mission Capital", program),
         program = ifelse(node == "E3 Alliance", "E3 Alliance", program),
         program = ifelse(node == "AmeriCorps", "AmeriCorps", program),
         level = 2) 

vertices <- bind_rows(nodes_outer, nodes_inner) |> 
  mutate(#radius = partnerships + 2,
         program = factor(program, names(program_colors))) |> 
  dplyr::distinct()

vertices$radius <- as.numeric(vertices$partnerships) ** 1.8/4

top_programs <- as.character(unique(vertices$program))

graph <- graph_from_data_frame(edges, vertices = vertices)

write.csv(edges, "data/processed/organization_connections.csv")

write.csv(nodes, "data/processed/organization_connections_total.csv")

```

## Formatting the Network Visualization 

```{r network_formatting}
windowsFonts(Georgia = windowsFont("Georgia"))


# create custom layout by updating existing circle layout
layout <- create_layout(graph, layout = 'circle')


outer_circle <- layout |>
  dplyr::filter(level == 1) |>
  dplyr::mutate(program = factor(program, names(program_colors))) |>
  dplyr::arrange(program, desc(name)) |>
  dplyr::mutate(
    x = cos((row_number() - 1) / number_of_nonprofits * 2 * pi),
    y = sin((row_number() - 1) / number_of_nonprofits * 2 * pi)
  )

# positioning circle centers manually by specifying polar coords
angles <- c(135, 100, 245, 330, 80, 35, 360) 
radii <- c(0.55, 0.85, 0.5, 0.65, 0.75, 0.6, 0.85)
centers <- tibble(x = radii * cos(angles / 180 * pi),
                  y = radii * sin(angles / 180 * pi))
inner_circle <- centers |>
  bind_cols(select(filter(layout, level == 2),-x,-y)) |>
  mutate(program = ifelse(name == "Mission Squared", "Mission Squared", program)) |>
  mutate(program = ifelse(name == "Mission Capital", "Mission Capital", program))

layout[] <- dplyr::bind_rows(outer_circle, inner_circle)

#Manually changing some of the points so that you can see the names 

 layout$x[layout$name == "Con Mi MADRE"] <- 0.8052703      	
 layout$y[layout$name == "Con Mi MADRE"] <- -0.5929079
 layout$x[layout$name == "Lake Travis ISD"] <- 0.9500711        	
 layout$y[layout$name == "Lake Travis ISD"] <- -0.3120334
 
 
 layout$x[layout$name == "Foundation Communities"] <- 0.766044443        	
 layout$y[layout$name == "Foundation Communities"] <- -0.64278761
 layout$x[layout$name == "Mainspring Schools"] <- 0.8936326       	
 layout$y[layout$name == "Mainspring Schools"] <- -0.44879918


 layout$x[layout$name == "College Forward"] <- -0.7163942        	
 layout$y[layout$name == "College Forward"] <- 0.69769574
 layout$x[layout$name == "Seton Healthcare Family"] <- -0.9798719        	
 layout$y[layout$name == "Seton Healthcare Family"] <- 0.1996271

  layout$x[layout$name == "Goodwill Central Texas"] <- -0.605609687        	
 layout$y[layout$name == "Goodwill Central Texas"] <- 0.79576184
 layout$x[layout$name == "The Austin Project"] <- -0.95331852        	
 layout$y[layout$name == "The Austin Project"] <- 0.3019666
 
   layout$x[layout$name == "YouthWorks"] <- 0.7522755        	
 layout$y[layout$name == "YouthWorks"] <- 0.65884862
 layout$x[layout$name == "Healthcare Workforce Alliance of Central Texas"] <- 1.00000000        	
 layout$y[layout$name == "Healthcare Workforce Alliance of Central Texas"] <- 0.00000000
 
 



layout <- dplyr::arrange(layout, .ggraph.index)


ggraph(layout) +
  geom_edge_diagonal(
    aes(edge_color = node1.program, edge_alpha = as.factor(main)),
    edge_width = 0.3,
    show.legend = FALSE
  ) +
  geom_node_point(aes(size = radius, color = program),
                  alpha = 0.6,
                  show.legend = FALSE) +
  scale_edge_color_manual(values = program_colors) +
  scale_color_manual(values = program_colors) +
  scale_size_area(max_size = 150) +
  scale_edge_alpha_manual(values = c(0.6, 1)) +
  coord_fixed() +
  geom_node_text(
     aes(
       x = 1.0175 * x,
       y = 1.0175 * y,
       label = ifelse(
         partnerships > 2, 
         name, 
         ""),
       angle = -((-node_angle(x, y) + 90) %% 180) + 90,
       filter = !(name %in% top_programs)
     ),
     size = 4, hjust = 'outward', family = 'Georgia'
   ) +
  geom_node_text(
    aes(
      x = x,
      y = y,
      label = name,
      filter = name %in% top_programs
    ),
    size = 6,
    hjust = 0.5,
    family = 'Georgia'
  ) +
  geom_node_text(
    aes(
      x = x,
      y = y - 0.045,
      label = ifelse(
        partnerships > 6,
        format(partnerships, big.mark = ','),
        partnerships
      ),
      filter = name %in% top_programs
    ),
    size = 5,
    hjust = 0.5,
    family = 'Georgia'
  ) +
   labs(title = 'Data Capacity Building Network in Central Texas',
        subtitle = 'By: Ethan Tenison, Project Manager for RGK Data Initiatives') +
  theme_void() +
  theme(
    text = element_text(family = 'Georgia'),
    legend.position = c(0.645, 0.51),
    plot.title = element_text(
      face = 'bold',
      hjust = 0.5,
      size = 20,
      margin = margin(t = 45, b = 3)
    ),
    plot.subtitle = element_text(
      face = 'plain',
      hjust = 0.5,
      size = 12,
      margin = margin(t = 5, b = 3)
    ),
    plot.margin = margin(0, 0, 0, 0, unit = "cm")
  )


ggsave(
  'reports/nonprofit_network_v2.png',
  width = 12,
  height = 12.5,
  dpi = 500
)
```

# Organizational Learning Data Spring 2021 

Gauging how organizations learned about different topics in data and evaluation. Some manual cleaning took place in excel.  

```{r org_survey}

library(RColorBrewer)
library(extrafont)
loadfonts(device = "win")

org_learning <- read_csv("data/raw/org_learning_spring2021.csv") |>
  select(Question, X4, X6, X8) |>
  pivot_longer(!Question, names_to = "answer", values_to = "n") |>
  mutate(
    percent = n / 14,
    answer = ifelse(answer == "X4", "Not applicable", answer),
    answer = ifelse(answer == "X6", "Somewhat True", answer),
    answer = ifelse(answer == "X8", "Very True", answer),
    answer = factor(
      answer,
      levels =
        c("Very True", "Somewhat True", "Not applicable"),
      exclude = NULL,
      ordered = TRUE
    )
  )




#Quesiton
org_learning$Question[org_learning$Question == "implement a measurement strategy for program evaluation"] <- "implement a\n measurement\n strategy"

org_learning$Question[org_learning$Question == "conduct surveys, focus groups, or stakeholder interviews"] <- "conduct surveys,\n focus groups,\n or interviews"

org_learning$Question[org_learning$Question == "use data for analysis, visualization, or reporting"] <- "use data\n for analysis\n or reporting"

org_learning$Question[org_learning$Question == "integrate advanced analytics into the organization's operations"] <- "integrate\n advanced\n analytics"

org_learning$Quesiton <- factor(
  org_learning$Question,
  levels =
    c("implement a\n measurement\n strategy", "conduct surveys,\n focus groups,\n or interviews", "use data\n for analysis\n or reporting", "integrate\n advanced\n analytics"),
  exclude = NULL,
  ordered = TRUE
)


#Ggplot 
theme_set(theme_classic())

g <- ggplot(org_learning, aes(x = Question, y = percent, fill = answer)) +
  geom_bar(stat = "identity") +
   geom_text(aes(label = paste(format(
     round(percent, 3)*100, nsmall = 1
   ), "%"), y = percent),
   position = position_stack(vjust = 0.5),
   size = 8) +
  coord_flip()+
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.background = element_rect(fill = "#D6D6D6"),
    axis.line = element_blank(),
    text = element_text(
                        size = 30,
                        face = "bold"),
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    axis.ticks = element_blank(),
     axis.text.x=element_blank(),
    plot.title = element_text(hjust = 0.5),
    plot.margin = margin(10, 10, 10, 10),
    plot.background = element_rect(fill = "#D6D6D6"),
    legend.title = element_blank(),
    legend.position = "bottom",
    legend.background = element_rect(fill = "#D6D6D6"), 
    
  ) +
  scale_fill_manual(values = c("#487897", "#7EACCD", "#F6AC75")) +
  labs(title = "CONNECT helped\n my organization learn how to...", y = "Number Answered", fill = "Response") #+


g

ggsave(
  "./reports/organization_learning_summer2021.png",
  dpi = 500 ,
  width = 14,
  height = 9,
  units = "in"
)

```